Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-13 papers/assembly/I/main.tex
Clarify a point about elements of N[X].

The collection of such formal linear combinations is referred to as the \textit{free commutative monoid} on $X$ over the natural number $\N$, and is typically denoted $\N[X]$.
The set $X$, in this context, is referred to as the set of generators of $\N[X]$.
An element $a \in \N[X]$ can be written as
\begin{equation*}
    a = \sum_{x \in X} a_x x
\end{equation*}
with natural number coefficients $a_x$, only finitely many non-zero.
This construction naturally has a monoidal structure, hence the name.
You can add such linear combinations to gether, e.g. $\ce{H_2} + (\ce{H_2} + \ce{O_2}) = \ce{2H_2} + \ce{O_2}$, and there exists an identity element $0$ such that $0 + a = a + 0 = a$ for all $a \in \N[X]$.
It is important to stress at this point that the linear combinations do not need to ``make sense'', at least not yet.
Taking the molecular example, $\ce{H_2}$, $\ce{7H_2} + \ce{O_2}$ and $\ce{H_2} + \ce{H_2O} + \ce{O_2}$ are permissible linear combinations and so are elements of $\N[X]$.
This does not mean that we will, in practice, consider all of them.
Restrictions on which linear combinations are consider will come into the picture when we introduce transitions.

>>>>

The collection of such formal linear combinations is referred to as the \textit{free commutative monoid} on $X$ over the natural number $\N$, and is typically denoted $\N[X]$.
The set $X$, in this context, is referred to as the set of generators of $\N[X]$.
An element $a \in \N[X]$ can be written as
\begin{equation*}
    a = \sum_{x \in X} a_x x
\end{equation*}
with natural number coefficients $a_x$, only finitely many non-zero.
This construction naturally has a monoidal structure, hence the name.
You can add such linear combinations to gether, e.g. $\ce{H_2} + (\ce{H_2} + \ce{O_2}) = \ce{2H_2} + \ce{O_2}$, and there exists an identity element $0$ such that $0 + a = a + 0 = a$ for all $a \in \N[X]$.
It is important to stress at this point that the linear combinations do not need to ``make sense'', at least not yet.
Taking the molecular example, $\ce{H_2}$, $\ce{7H_2} + \ce{O_2}$ and $\ce{H_2} + \ce{H_2O} + \ce{O_2}$ are permissible linear combinations and so they are elements of $\N[X]$.
This does not mean that we will, in practice, consider all of them.
Restrictions on which linear combinations are consider will come into the picture when we introduce transitions.
